Comparing binsegRcpp with other implementations of binary segmentation for changepoint detection

### 2025-05-02 article.Rnw
rpt

%% - \Abstract{} almost as usual
\Abstract{ Binary segmentation is a classic algorithm for detecting
  changepoints in sequential data. In theory, using a simple loss
  function like Gaussian or Poisson, binary segmentation should be
  extremely fast for $N$ data and $K$ segments, $O(N K)$ in the worst
  case, and $O(N \log K)$ in the best case. In practice existing
  implementations such as ruptures (\proglang{Python} module) and
  changepoint (\proglang{R} package) are much slower, and in fact
  sometimes do not return a correct result. We present the
  \proglang{R} package \pkg{binsegRcpp}, which provides an efficient
  C++ implementation of binary segmentation, and always returns
  correct results. We discuss some C++ coding techniques
  which were used to avoid repetition, for efficiency, and for
  readability.  We additionally include detailed theoretical and
  empirical comparisons with other implementations of binary
  segmentation in \proglang{R} packages \pkg{fpop}, \pkg{blockcpd} and
  \pkg{wbs}. }

>>>>

%% - \Abstract{} almost as usual
\Abstract{ Binary segmentation is a classic algorithm for detecting
  changepoints in sequential data. In theory, using a simple loss
  function like Gaussian or Poisson, binary segmentation should be
  extremely fast for $N$ data and $K$ segments, $O(N K)$ in the worst
  case, and $O(N \log K)$ in the best case. In practice, existing
  implementations such as \pkg{ruptures} (\proglang{Python} module) and
  \pkg{changepoint} (\proglang{R} package) are substantially slower.
  Additionally, \pkg{changepoint} sometimes returns incorrect results.
  We present the \proglang{R} package \pkg{binsegRcpp}, which provides an efficient
  and correct C++ implementation of binary segmentation.
  We discuss some C++ coding techniques
  which were used to avoid repetition, for efficiency, and for
  readability.  We additionally include detailed theoretical and
  empirical comparisons with other implementations of binary
  segmentation in other packages: \pkg{ruptures}, \pkg{fpop}, \pkg{changepoint} and
  \pkg{wbs}. }
